\section{Introduction}
\label{chap:Introduction}

\quad The purpose of this project was to get comfortable with word embeddings, integrate pre-trained embeddings in neural architecture, and implement a recurrent neural network for a classification task.


\subsection{Source code}
\label{chap:Source code}

\quad \, All code made for this project is written in Python v.3.9, and found in the GitHub repository at \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2}{https://github.uio.no/fabior/IN5550/tree/master/Oblig2}. The repository contains:

\begin{itemize}


\item \href{https://github.uio.no/fabior/IN5550/blob/master/Oblig2/evaluation.py}{\texttt{evaluation.py}} - Python file provided the instructors will use to compare the prediction results with their gold standards.


\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/ex4.py}{\texttt{ex4.py}} - Code for exercise 4

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/ex5.py}{\texttt{ex5.py}} - Code for exercise 5

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/ex6.py}{\texttt{ex6.py}} -Code for exercise 6

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/data}{\texttt{data/}} - Directory containing the data utilized in this project.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/outputs}{\texttt{outputs/}} - Directory containing the collection of tuning results.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/packages}{\texttt{packages/}} - Directory containing the collection of Python methods utilized in the project.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/packages/ann_models.py}{\texttt{packages/ann\_models.py}} - Python file containing both the feed neural network and the recurrent neural network models.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/packages/studies.py}{\texttt{packages/studies.py}} - Python file containing the studies used for tuning hyper-parameters on the MLP model.

\item \href{https://github.uio.no/fabior/IN5550/blob/master/Oblig2/packages/plot.py}{\texttt{packages/plot.py}} - Python file used for plotting the results found in tuning step.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/packages/preprocessing.py}{\texttt{packages/preprocessing.py}} - Python file containing classes that load, split, and preprocess the data.

\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/rnn_studies.py}{\texttt{packages/rnn\_studies.py}} - Python file containing studies written to tune the parameters of the RNN model.

\item \href{https://github.uio.no/fabior/IN5550/blob/master/Oblig2/predict_on_test.py}{\texttt{predict\_on\_test.py}} - The file used to generate the results for evaluation



\item \href{https://github.uio.no/fabior/IN5550/tree/master/Oblig2/report}{\texttt{report/}} - Directory containing the written report in latex and pdf.

\end{itemize}